%\title{My two column CV}
%
% tccv (two columns curriculum vitae) is a LaTeX class inspired by
% the template found at latextemplates.com by Alessandro Plasmati.
%
% Create by Nicola Fontana, the original files can be downloaded from:
% http://dev.entidi.com/p/tccv/
%
\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}

\part{QIU Yuan}

\section{Work experience}

\begin{eventlist}

\item{Feb 2018 -- May 2018}
     {Computer Science Department, HKUST}
     {Teaching assistant}

Course: Design and Analysis of Algorithms \newline (COMP 3711)\\
Taught weekly tutorials.\\
Graded assignments and exam papers.\\
Worked with algorithm related materials. \\
Achieved 80.0\% in student feedback evaluaion.

\item{Sept 2017 -- Dec 2017}
     {Computer Science Department, HKUST}
     {Teaching assistant}

Course: Honors Design and Analysis of Algorithms \newline (COMP 3711H)\\
Taught weekly tutorials.\\
Graded assignments and exam papers.\\
Worked with algorithm related materials.\\
Achieved 91.3\% in student feedback evaluation.

\item{Feb 2017 -- May 2017}
     {Computer Science Department, HKUST}
     {Lab Helper}

Course: OOP and Data Structures (COMP 2012)\\
Helped students with lab tasks.\\
Worked with C++ related materials.

\item{Jan 2016 -- Aug 2017}
     {URAO, HKUST}
     {Student Ambassador}

Led campus tours for incoming visits.\\
Participated in recruitment events and student talks.

\item{Oct 2015 -- Nov. 2015}
     {Math Department, HKUST}
     {MATH Tutor}

Helped students with homework problems. \\
Worked with Calculus, Linear Algebra, Probability and Statistics.

\end{eventlist}

\section{Research Projects}

\begin{yearlist}

\item{2016}
     {WiFi Tracking and User Analytics}
     {Final Year Undergraduate Project \newline Supervised by Prof. Gary Chan}

\item{2014}
     {Direction-Based Trajectory \newline Simplification}
     {UROP Project \newline Supervised by Prof. Raymond Wong}

\end{yearlist}

\personal
    [QiuTedYuan.github.io]
    {104D, Tower A, HKUST\newline Clear Water Bay, Kowloon, Hong Kong}
    {+852 5299 2788}
    {yqiuac@cse.ust.hk}

\section{Education}

\begin{yearlist}

\item[HKUST]{2017 -- Present}
     {MPhil in Computer Science}
     {Supervised by Prof. Ke Yi}

\item[HKUST]{2013 -- 2017}
     {Bsc in Math and Economics, and in Computer Science}
     {First Class Honors}

\end{yearlist}

\section{Communication skills}

\begin{factlist}
\item{Mandarin}{Native}
\item{English}{Good}
\item{Cantonese}{Fair}
\end{factlist}

\section{Software skills}

\begin{factlist}

\item{Good level}
     {C++, HTML/CSS, Java/JS, Spark, Scala, Unix, Python, Emacs}

\item{Intermediate}
     {\LaTeX, MySQL, git}

\item{Basic level}
     {PostgreSQL, Vim}

\end{factlist}

\section{Awards}

\begin{yearlist}

\item{2018}
     {Postgraduate Studentship}
     {HKUST}

\item{2017}
     {Academic Achievement Medal}
     {HKUST}

\item{-}
     {Reaching Out Award}
     {HKSAR Government}

\item{-}
     {\em \small{Chern-Class} \em Achievement Scholarship}
     {Math Department, HKUST}
     
\item{2016}
     {\small{First Runner-up in UG Math Competition}}
     {Math Department, HKUST}     

\item{-}
     {Epsilon fund award}
     {Math Department, HKUST}     


\item{2015}
     {The Cheng Foundation Scholarship}
     {Cheng Foundation}

\item{2013}
     {Kerry Holdings Limited Scholarship}
     {Kerry Holdings }
 
\end{yearlist}

\end{document}
